\texttt{SuperScreen}: An open-source package for simulating the magnetic response of two-dimensional superconducting devices

### 2021-11-09 main.tex

\begin{figure}
    \centering
    \includegraphics[width=\textwidth]{examples/images/pearl.pdf}
    \caption{Vortex field profiles calculated with \SuperScreen agree to within a few percent with the analytical solution (Eq.~\ref{eq:pearl}). (a) Cross section along the $x$-axis of the out-of-plane magnetic field $\mu_0H_z$ from a vortex located at the origin, $x=y=z=0\,\mu\mathrm{m}$ in a superconducting film, evaluated at a vertical distance $z=1\,\mu\mathrm{m}$ above the film for several different effective penetration depths $\Lambda$. (b) Cross-section along the $z$-axis of $\mu_0H_z$ from a vortex located at the origin, evaluated at $x=y=0\,\mu\mathrm{m}$, directly above the center of the vortex (logarithmic $y$ axis scale). In (a) and (b), the results from \SuperScreen are shown as open circles and the results from the Fourier transform method are shown as solid lines. (c) Percentage difference between the $\mu_0H_z$ calculated with \SuperScreen and the Fourier transform method for the $x$-axis cut shown in (a). (d) Percentage difference between the $\mu_0H_z$ calculated with \SuperScreen and the Fourier transform method for the $z$-axis cut shown in (b).}
    \label{fig:pearl}
\end{figure}

>>>>

\begin{figure}
    \centering
    \includegraphics[width=\textwidth]{examples/images/pearl.pdf}
    \caption{Vortex field profiles calculated with \SuperScreen agree to within a few percent with the analytical solution (Eq.~\ref{eq:pearl}). (a) The fluxoid $\Phi_S^f$ for a circular region in the film with radius $r=1\,\mu\mathrm{m}$ centered at the position of the vortex core, as a function of the film's effective penetration depth $\Lambda$. As $\Lambda$ increases, so to does the supercurrent contribution to the fluxoid. (b) Error in the total simulated fluxoid relative to $\Phi_0$: $(\Phi_S^f(\Lambda) - \Phi_0) / \Phi_0$. (c) Cross section along the $x$-axis of the out-of-plane magnetic field $\mu_0H_z$ from a vortex located at the origin, $x=y=z=0\,\mu\mathrm{m}$ in a superconducting film, evaluated at a vertical distance $z=1\,\mu\mathrm{m}$ above the film for several different effective penetration depths $\Lambda$. (d) Percentage difference between the $\mu_0H_z$ calculated with \SuperScreen and the Fourier transform method for the $x$-axis cut shown in (c). (e) Cross-section along the $z$-axis of $\mu_0H_z$ from a vortex located at the origin, evaluated at $x=y=0\,\mu\mathrm{m}$, directly above the center of the vortex (logarithmic $y$ axis scale). (f) Percentage difference between the $\mu_0H_z$ calculated with \SuperScreen and the Fourier transform method for the $z$-axis cut shown in (e). In (a) and (b), the results from \SuperScreen are shown as open circles and the results from the Fourier transform method are shown as solid lines. }
    \label{fig:pearl}
\end{figure}
